---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TEP

<!-- badges: start -->
<!-- badges: end -->

**TEP** provides tools to assess and visualize **temporal efficacy on mortality hazard**.
It estimates **time-varying hazard rates and hazard ratios** based on smoothed baseline hazards, along with their associated **confidence intervals (CI)** using both **asymptotic and bootstrap-based** inference.
To improve numerical stability in small-sample or rare-event settings, TEP incorporates **small-sample regularization via jittered data augmentation**.



## Installation

You can install the development version from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("liu-dada/TEP")
```

## Example



```{r example}
library(TEP)
data(example_data_sig)
head(example_data_sig)

#Bootstrap hazard ratio

hr <- bshr(
data = example_data_sig,
contr = "Control",
var = "GTE",
n_boot = 100
)

#Plot hazard ratio

hrplot(hr, var = "GTE")

#Plot KM curve with band 
all_func(example_data_sig,var='GTE',contr = 'Control')

```


